|

### 2024-08-07 doc/paper.qmd
modified preparation code

## Step 2: Data Preparation
First, I checked the dataset for duplicate firm-year observations based on the combination of the Worldscope Permanent ID (`item6105`) and the fiscal year (`year_`) and confirmed that there were no duplicates present, ensuring the accuracy of the data for further analysis. As the original study does not specify the net income measure, `item1651` (Net Income before Preferred Dividends) was used as the variable for net income. This choice aligns with the final net income figure reported in the income statement, based on the Excel Industrials Template by @WRDS_Balancing_Model_2024.

To prepare the data sample in line with the methodology outlined in the paper, it is essential to follow the requirements, as instructed by @Leuz_2003. Firstly, countries with sufficient firm-year observations must be filtered. Each country should have at least 300 firm-year observations for certain key accounting variables, including total assets, sales, net income, and operating income. Secondly, firms with adequate consecutive data must be identified. Each firm must have income statement and balance sheet information for at least three consecutive years, where I focus on the same key variables as in the previous step. If a firm had at least three consecutive years of complete data at any point, all its data entries were retained in the final dataset.

>>>>

## Step 2: Data Preparation
In order to verify the pulle data, I checked the dataset for duplicate firm-year observations based on the combination of the Worldscope Permanent ID (`item6105`) and the fiscal year (`year_`) and confirmed that there were no duplicates present, ensuring the accuracy of the data for further analysis. As the original study does not specify the net income measure, `item1651` (Net Income before Preferred Dividends) was used as the variable for net income. This choice aligns with the final net income figure reported in the income statement, based on the Excel Industrials Template by @WRDS_Balancing_Model_2024.

To prepare the data sample in line with the methodology outlined in the paper, it is essential to follow the requirements, as instructed by @Leuz_2003. Firstly, countries with sufficient firm-year observations must be filtered. Each country should have at least 300 firm-year observations for certain key accounting variables, including total assets, sales, net income, and operating income. In this step, no countries were eliminated as all countries met the requirement, which aligns with the paper's overview of countries.

Additionally, firms with adequate consecutive data must be identified. Each firm must have income statement and balance sheet information for at least three consecutive years, with all key accounting variables mentioned above present. If a firm had at least three consecutive years of complete data at any point, all its data entries were retained in the final dataset. Therefore, only those countries and firms that meet these criteria for all specified variables are retained in the dataset.
